|

### 2023-02-08 paper.Rmd
Wed Feb  8 13:00:08 CET 2023: update-remote.sh
Wed Feb  8 19:08:36 CET 2023: update-remote.sh
Wed Feb  8 20:00:06 CET 2023: update-remote.sh

# energy (cooling)
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/energyCooling_2hl_maxIndSize_fullRun_30gens/re_evaluate_energyCooling_2hl_maxIndSize_fullRun_30gens.sh

@@

...hier einfügen...

>>>>

# energy (cooling)
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/energyCooling_2hl_150hn_fullRun_30gens/re_evaluate_energyCooling_2hl_150hn_fullRun_30gens.sh

@@

```{r statutory_declaration, echo=FALSE}
knitr::include_graphics("~/masterThesis/master_thesis/private/statutory_declaration.pdf")
```
